Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-15 ms.tex
more text, more references

%basic background about interstellar dust emission

%maybe say instead ``over the past 30/40 years...''
%Barnard first recognized evidence for dust in astronomical observations, and
%ever since it has been mapped in increasing detail. 
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. IRAS, with its $\sim$6$'$ 
resolution, revolutionized the study of Galactic dust emission, first revealing
 the high-latitude ``infrared cirrus'' using \IRAS~60$\mu$m and 100$\mu$m 
observations \citep{low84, wheelock94}. Beginning in 1989, DIRBE  mapped the 
full sky at ten infrared wavelengths from 1.25$\mu$m to 240$\mu$m with a 
reliable zero point, but inferior 0.7$^{\circ}$ angular resolution 
\citep{boggess92}.mention FIRAS specifically, since it is important to FDS99.

FDS99 used FIRAS to make a globally best-fit model of dust emission 
appropriate over a very broad range of frequencies. They showed that a 
model consisting of a single MBB with power law index $\beta$ 
could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
a spectrum consisting of two MBBs, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
silicates and carbonaceous grains.

@@

%For each pixel on the sky, Planck thus provides us with four data points of 
%the dust emission SED. The angular resolution of these maps is $5.5$.

@@

%\subsection{Zodiacal Light}
%As mentioned above, we rely upon the \cite{planckzodi} zodiacal light 
%correction.

@@

% what about the instrumental noise n_{\nu_i} ---> can't find anything
% in planck literature ... nevermind n^2 <-> ii_cov in binary tables

@@

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{Comparison of SFD temperature, two-component model $T_2$, and 
\cite{planckdust} temperature. Note the differing colorscales. Both models 
incorporating \PLANCK~data clearly show a major improvement in resolution 
relative to SFD.}
\end{center}
\end{figure}

@@

\subsection{Limitations}
% CIBA !!!
% IRAS missing so that parts of sky not truly 6.1' resolution map

\subsection{Comparison to Planck Collaboration Dust Map}
%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
An important difference between our maps and those of \cite{planckdust} is our 
use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}.

>>>>

%basic background about interstellar dust emission
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. IRAS, with its $\sim$6$'$ 
resolution, revolutionized the study of Galactic dust emission, first revealing
 the high-latitude ``infrared cirrus'' using \IRAS~60$\mu$m and 100$\mu$m 
observations \citep{low84, wheelock94}. Beginning in 1989, DIRBE  mapped the 
full sky at ten infrared wavelengths from 1.25$\mu$m to 240$\mu$m with a 
reliable zero point, but inferior 0.7$^{\circ}$ angular resolution 
\citep{boggess92}.mention FIRAS specifically, since it is important to FDS99.

FDS99 used FIRAS \citep{firas} to make a globally best-fit model of dust 
emission appropriate over a very broad range of frequencies. They showed that 
a model consisting of a single MBB with power law index $\beta$ 
could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
a spectrum consisting of two MBBs, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
silicates and carbonaceous grains.

@@

@@

@@

@@

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
model $T_2$, and \cite{planckdust} temperature. Note the differing colorscales.
Both models incorporating \PLANCK~data clearly show a major improvement in 
resolution relative to SFD.}
\end{center}
\end{figure}

@@

\subsection{Limitations}
Perhaps the dominant limitation of our fits is the presence of cosmic
infrared background anisotropies (CIBA) bleeding through into our maps of 
Galactic dust temperature and optical depth in high-latitude regions 
\citep{ciba}.
% CIBA !!!
% IRAS missing so that parts of sky not truly 6.1' resolution map

\subsection{Comparison to Planck Collaboration Dust Map}
%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
An important difference between our maps and those of \cite{planckdust} is our 
use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
clearly visible in the \cite{planckdust} maps.

%we actually have 6.1' arcminute smoothing
It is true that we have smoothed the input intensity maps for this study 
to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
\cite{planckdust} maps. However, as is apparent from figure 
\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.
